Climate Perceptions in Toronto

### 2021-04-04 outputs/paper/paper.Rmd
incl paper sections

---
title: "Climate Perceptions in Toronto"
author: "Lorena Almaraz De La Garza"
date: "2021 04 19"
output:
  bookdown::pdf_document2: default
subtitle: "with data from Open Data Toronto"
toc: FALSE
thanks: 'Code and data are available in this GitHub repository: [lalmaraz/toronto_climate_perceptions] (https://github.com/lalmaraz/toronto_climate_perceptions).'
bibliography: references.bib
abstract: X
---

# Introduction

```{r libs, include = FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# Load libraries
library(bookdown)
library(ggmap)
library(gt)
library(here)
library(httr)
library(janitor)
library(kableExtra)
library(knitr)
library(opendatatoronto)
library(readxl)
packageVersion("readxl")
library(rio)
library(tidyverse)

# Find and get data

questions <- search_packages("climate") %>% 
  list_package_resources() %>% 
  filter(grepl("Readme Data Field Names", name)) %>% 
  get_resource()

raw_data <- search_packages("climate") %>% 
  list_package_resources() %>% 
  filter(grepl("City of Toronto Climate Perceptions SPSS v1", name)) %>% 
  get_resource()

# Save data
write_csv(raw_data,"inputs/data/raw_data.csv")

# Read in data
all_data <- read_csv("inputs/data/raw_data.csv")
```

@@

@@

## Limitations

## Next Steps

\newpage
# Appendix 1 {#appendix1}
```

>>>>

---
title: "Climate Perceptions in Toronto"
author: "Lorena Almaraz De La Garza"
date: "April 19th, 2021"
keywords: "X, Y, Z"
output:
  bookdown::pdf_document2: default
subtitle: "with data from Open Data Toronto"
toc: FALSE
thanks: 'Code and data are available in this GitHub repository: [lalmaraz/toronto_climate_perceptions](https://github.com/lalmaraz/toronto_climate_perceptions).'
bibliography: references.bib
abstract: "The abstract text occupies this beautiful space right here. \\par
 \\textbf{Keywords:} search, stackoverflow, find, workaround"

---

```{r libs, include = FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# Load libraries
library(bookdown)
library(ggmap)
library(gt)
library(here)
library(httr)
library(janitor)
library(kableExtra)
library(knitr)
library(opendatatoronto)
library(readxl)
library(rio)
library(tidyverse)
```

# Introduction
[@R]

@@

## Methodology
## Results

@@

## Findings
## Implications
## Limitations
## Future Work

```{r echo=FALSE, message=FALSE, warning=TRUE}

```

\newpage
# Appendix 1 {#appendix1}
